Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-11 arxiv/intro.tex
revision

\section{Introduction}

@@

\paragraph{Organizations.}
\todo{revise} The appendix is organized as follows.
In Section \ref{app_proof_sec3}, we describe an extended background and a further reivew of related work.
In Section \ref{app_proof_main_thm}, we present the analysis of the bias-variance tradeoff for the case of two tasks.
In Section \ref{app_iso_cov}, we illustrate the above analysis in simplified settings including the isotropic model and covariate shifted settings without model distance.
In Section \ref{app_proof_many_tasks}, we extend our analysis to many tasks with the same features.
In Section \ref{sec_maintools}, we prove the bias and variance bounds used in the analysis.
Finally in Section \ref{app_experiments}, we fill in the missing details of our experiments.

>>>>

\section{Introduction}\label{sec introduction}

@@
